Synchrotron X-Ray Rims in Tycho's Supernova Remnant are Energy Dependent

### 2014-10-04 manuscript/paper-tycho.tex
Start B-damping port; paper discussion
Clean up B-damping model + identify differences to port
Flesh out results, discussion, conclusion

\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mt{E}}
\newcommand*{\Ecut}{E_{\mt{cut}}}
\defcitealias{ressler2014}{R14}

@@

\begin{abstract}
\note[Aaron]{Clone of AAS abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  Synchrotron loss-limited
rim widths should decrease with energy whereas damping limited rims should be
relatively energy-independent.  To discriminate between models, we measured rim
widths around Tycho's supernova remnant in 5 energy bands using an archival
$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
favoring loss-limited radiation over magnetic damping and corroborating similar
observations in the remnant of SN 1006. Observed widths are best fit by
electron transport models requiring amplified magnetic fields of
$\abt200$--$1000 \unit{\mu G}$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
Non-negligible diffusion results in some degeneracy between magnetic field
strength and diffusion coefficient in setting observed rim widths, but strong
magnetic fields are required for all measurements.  A different approach may be
needed to better constrain diffusion at supernova remnant shocks.
\end{abstract}

@@

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
\note[Aaron]{question: which came first?  observation of synchrotron
steepening, or explanation/prediction of electron cut-off and hence synchrotron
roll-off?  Or, even, was the electron cut-off predicted but the observable
consequence of synchrotron roll-off not recognized until observations?} Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{miniati2000, ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

@@

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from an
archived \Chandra large project (PI: J. Hughes) also allows us to sample the
remnant rims quite finely.  Furthermore, Tycho has been a prime target of study
for determining whether hadrons are being accelerated in historic SNRs
\citep[and references therein]{morlino2012}; understanding the acceleration
process will bear upon our understanding of CR acceleration in Tycho.
\note[Aaron]{reword/cut?}

@@

\note[Aaron]{I am a bit uncertain on the structure/order of presentation here,
particularly in presenting $\Ecut$ (which can be an independent observable?
but is not considered here).  I tried to put ``enough'' to independently
follow / re-derive all the model results.}
% TODO Chunk of text I don't know what to do with...
We consider two models for particle transport to our measurements of Tycho's
filament widths.  To best quantify width-energy dependence, we measure rim full
widths at half maximum (FWHMs) (Section~\ref{sec:fwhms}) and fit the
measurements to these models' predictions of rim FWHMs at multiple photon
energies.  \citetalias{ressler2014} give a fuller review of previous approaches
to characterizing filament widths, as well as a more thorough exposition of
model parameters and physical implications.

We use CGS (Gaussian) units throughout.

Any other introductory text -- emphasize that we back out two parameters,
possibly three or more.  COME BACK after writing magnetic damping bit.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc (somewhere state that CGS
%      notation is being used)
% TODO double check equations, exposition against Rettig/Pohl and others
% TODO review variable definitions when closer to final draft
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose much material is not relevant or
condensed into our diffusion coefficient $D$ (w/ stated Bohm diffusion).
Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

@@

% Moving on...
In what follows we consider both transport models, but primarily present
results from the more advanced model (equation~\eqref{eq:full-mod}) as we find
that the qualitative behavior of both models is comparable.

@@

Much previous work has assumed Bohm-like diffusion in plasma downstream of the
shock.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
all energies.
\note[Aaron]{for self-edification, any justification / derivation of this
result?  All the papers seem to take it for granted}
However, different types of MHD turbulence may give rise to a non-linear energy
scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
quasi-linear approximation for particle motion,
\note[Aaron]{I don't really know what this means}
predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
I have no idea what this means.}

In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has unites
of $\mathrm{erg}^{1-\mu}$.
The right-hand side of equation~\eqref{eq:diffcoeff} introduces a dimensionless
$\eta_h$ as the diffusion coefficient scaled to the Bohm value at a fiducial
particle energy $E_h$.  We subsequently choose the fiducial electron energy
$E_h$ corresponding to a synchrotron photon energy of $2 \unit{keV}$, taking
the $\delta$-function approximation that an electron of energy $E$ radiates
solely at frequency $\nu \propto E^2 B$ in a surrounding magnetic field.  Then,
$E_h \propto \sqrt{2 \unit{keV} / B}$.  Although the value of $E_h$ depends on
magnetic field $B$, tying $\eta_h$ to a fixed observation energy gives a
convenient and intuitive sense of diffusion strength regardless of the
electron energies producing observed rims.
\note[Aaron]{what I want to say: electron energies responsible for the rims we
see could vary between remnants or even within a single remnant.  And, we
cannot get a handle on diffusion at a singular electron energy or energy range,
in all our observations.  So it's simpler to tie $\eta_h$ to observation
energy.}

With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated, so the energy spectrum drops off steeply.  The cut-off energy
adapted from \citet{parizot2006} is given as:
\begin{align}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \unit{\mu G}}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
Note that this expression implicitly assumes (1) a strong shock with
compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
downstream; see \citet{parizot2006} for a full derivation.

@@

\subsection{Width-energy dependence}

As discussed in Section~\ref{sec:intro}, width-energy dependence is key to
differentiating between loss/diffusion-limited rims and magnetically damped
rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
terms of a scaling exponent $\mE$ defined by:
\begin{equation}
    w(\nu) \propto \nu^{\mE}
\end{equation}
where $w(\nu)$ is filament FWHM as a function of observed photon frequency
$\nu$, and $\mE = \mE(\nu)$ is generally energy dependent.  We may refer to
observed photons interchangeably by energy or frequency $\nu$; however, $E$ is
reserved for electron energy.

If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -0.5$; this is the
strongest energy-dependence possible in our models.  Diffusion increases $\mE$
monotonically but roughly plateaus at values between $-0.4$ and $0$, with
larger $\mu$ values yielding weaker energy-dependence ($\mE$ closer to $0$, or
even positive) \citepalias[Figure 3]{ressler2014}.

@@

\subsection{Previous studies of Tycho}

\note[Aaron]{Should we follow \citet{ressler2014} in adding a table of prior
magnetic field estimates? This could be placed here, in the intro, or in the
discussion.}
\citet{parizot2006} derive magnetic fields of $300$--$500 \unit{\mu G}$; they
also give both diffusion coefficients (in their $k_0$?) and $\Ecut$ values.
\citet{rettig2012} used a measured filament lengthscale and considered
loss-limited and magnetic damping models separately for several historical
SNRs.  For Tycho: they report $B = 310 \unit{\mu G}$ with $\Ecut = 24
\unit{TeV}$; since $\Ecut$ is set by balancing advective/diffusive
lengthscales, this is equivalent to our reporting of a diffusion coefficient
(?).  With magnetic damping, they report $B = 150 \unit{\mu G}$ and a larger
$\Ecut = 34 \unit{TeV}$.  Taken from \citet{rettig2012}: \citet{acciari2011}
give $80$, $230 \unit{\mu G}$ for leptonic/hadronic models for gamma-ray
emission in Tycho.

@@

We fit spectra from each region's upstream and downstream sections to an
absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) between $0.5$--$7
\unit{keV}$ with photon index $\Gamma$, hydrogen column density $N_{\mt{H}}$,
and a normalization as free parameters.  Table~\ref{tab:spec} lists best fit
parameters and reduced $\chi^2$ values for all regions.  Spectra from thin rims
(upstream sections) are well-fit by the power law model alone; spectra from
sections downstream of the rims are generally poorly-fit, reflecting thermal
contamination primarily from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line
emission at $1.85$ and $2.45$ keV.  Although most downstream spectra show
thermal contamination, some regions (e.g., ?!?!, ?!?! on Tycho's northwestern limb)
are reasonably well-fit downstream due to a larger gap between the forward
shock and contact discontinuity.
Our best-fit photon indices ($2.4$--$3$) and column densities ($0.6$--$0.8
\times 10^{22} \unit{cm^{-2}}$) from upstream spectra are consistent with
previous spectral fits to Tycho's nonthermal rims \citep{hwang2002,
cassam-chenai2007}.
% NOTE keep stated ranges of spectral indices, column densities up to date
% NOTE keep example region numbers up to date

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
and the stretched or compressed FWHMs as upper/lower bounds on our reported
FWHMs.

@@

% Model knobs and how we twiddled them
We varied three physical parameters (more if we consider magnetic damping fits
explicitly):
diffusion-energy scaling exponent $\mu$, normalized diffusion
coefficient $\eta_2$, and magnetic field strength $B_0$.
To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$;
recall that $\mu = 1/3$ and $1/2$ correspond to Kolmogorov and Kraichnan turbulence.

% Tycho parameters
A few remnant-specific parameters enter into the model calculations.  We
adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha = 0.65$
\note[Aaron]{will change to $s= 2.16$ from $\alpha=0.58$ following
\citet{sun2011} on next iteration}
\citep{kothes2006},
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and
shock radius $1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolated shock velocities reported by
\citet{williams2013} (rescaled to $3 \unit{kpc}$ rather than $2.3 \unit{kpc}$
to estimate individual shock velocities for each region.

@@

\begin{table*}[ht]
    \scriptsize
    \centering
    \caption{Measured full widths at half max (FWHMs) for all regions.
             \label{tab:fwhms}}
    \input{tab-fwhms.tex}
\end{table*}

@@

The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
reflecting the high quality of underlying \Chandra data as also seen in
Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
part to (1) our profile fitting procedure, which depends on an empirically
chosen profile fit function which may also fit the rims non-uniquely, and (2)
variation in Tycho's rim morphology, also demonstrated clearly in
comparison of rims from Regions 1 and 16 in Figure~\ref{fig:profiles}.
\note[Aaron]{review paragraph wording}

>>>>

\defcitealias{ressler2014}{R14}
\newcommand*{\Chandra}{\textit{Chandra}\ }
\newcommand*{\tsynch}{\tau_{\mt{synch}}}
\newcommand*{\mE}{m_\mt{E}}
\newcommand*{\Ecut}{E_{\mt{cut}}}
\newcommand*{\muG}{\unit{\mu G}}

@@

\begin{abstract}
\note[Aaron]{Clone of AAS abstract}
Several young supernova remnants exhibit thin X-ray bright rims of synchrotron
radiation at their forward shocks.  Thin rims have been taken to indicate that
shock-accelerated electrons rapidly cool downstream of the shock, requiring
strong magnetic field amplification.  But, magnetic field damping immediately
behind the shock could produce similarly thin rims.  Synchrotron loss-limited
rim widths should decrease with energy whereas damping limited rims should be
relatively energy-independent.  To discriminate between models, we measured rim
widths around Tycho's supernova remnant in 5 energy bands using an archival
$750 \unit{ks}$ \Chandra observation.  Rims narrow with increasing energy,
favoring loss-limited radiation over magnetic damping and corroborating similar
observations in the remnant of SN 1006. Observed widths are best fit by
electron transport models requiring amplified magnetic fields of
$\abt200$--$1000 \muG$ and particle diffusion coefficients $\abt
1$--$100\times$ Bohm values, consistent with prior work on Tycho's SNR.
Non-negligible diffusion results in some degeneracy between magnetic field
strength and diffusion coefficient in setting observed rim widths, but strong
magnetic fields are required for all measurements.  A different approach may be
needed to better constrain diffusion at supernova remnant shocks.
\end{abstract}

@@

% What can we learn from these shocks?  Why are they interesting?
Spectral and spatial measurements of synchrotron rims can constrain physical
parameters of the shock acceleration process.  Many previous workers have
inferred strong magnetic field amplification at SNR shocks, as electrons must
rapidly radiate energy to account for the thinness of observed rims
\citep{bamba2003, vink2003, parizot2006}.  Furthermore, broadband synchrotron
synchrotron flux from supernova remnants steepens at X-ray energies
\citep{reynolds1999}, corresponding to a cut-off in the underlying electron
spectrum as predicted by diffusive shock acceleration \citep{webb1984}.
\note[Aaron]{question: which came first?  observation of synchrotron
steepening, or explanation/prediction of electron cut-off and hence synchrotron
roll-off?  Or, even, was the electron cut-off predicted but the observable
consequence of synchrotron roll-off not recognized until observations?} Many
fundamental questions about the shock acceleration process remain to be
answered.  Under what conditions do shocks accelerate particles efficiently?
How are magnetic fields amplified in such shocks?  \citet{reynolds2008} reviews
relevant observations and open questions to date.  The answers to these
questions are broadly relevant to many astrophysical shocks, such as Earth's
bow shock, stellar wind-blown bubbles, starburst galaxies \citep{heckman1990},
jets of active galactic nuclei, galaxy clusters \citep{van-weeren2010}, and
even cosmological shocks \citep{ryu2008}.
% Expand on these questions -- plasma turbulence, Alfven waves, wave damping
% behind the shock, upstream/downstream plasma interactions and instabilities
% These in turn affect plasma, CR dynamics -- how does the shock propagate and
% interact with the ISM?  Will we see a precursor due to diffusion and/or CR
% streaming?  How efficiently are CRs accelerated?

@@

% Why Tycho's SNR
To further test these models, we follow \citet{ressler2014} (hereafter,
\citetalias{ressler2014}) by measuring rim widths at multiple energies in the
remnant of Tycho's 1572 supernova (hereafter, Tycho).  Tycho exhibits an
extensive shell of synchrotron-dominated thin rims around its periphery; the
rims show very little thermal emission, consistent with expansion into a low
density ISM \citet{williams2013}.  Tycho, being a nearby galactic SNR, is close
enough that its rims are easily resolved by \textit{Chandra} spatial
resolution. A deep $750 \unit{ks}$ exposure of the entire remnant from 2009
(PI: J. Hughes) also allows us to sample the remnant rims quite finely.
Furthermore, Tycho has been a prime target of study for determining whether
hadrons are being accelerated in historic SNRs \citep[and references
therein]{morlino2012}; understanding the acceleration process will also bear
upon our understanding of CR acceleration in Tycho.
\note[Aaron]{can reword/cut?}

@@

We consider two particle transport models that we fit to measurements of
Tycho's thin rim widths.  We measure the rim full widths at half maximum
(FWHMs) (Section~\ref{sec:fwhms}) and use the measurements to directly assess
width-energy dependence.  The measurements are also fit to the transport
models' predictions of rim FWHMs at multiple photon energies.  The models
accept three free parameters: magnetic field strength $B_0$, a scaled diffusion
coefficient $\eta_2$, and a diffusion-energy scaling exponent $\mu$.

We use CGS (Gaussian) units throughout.  Our presentation is somewhat
abbreviated; please refer to \citetalias{ressler2014} for a fuller review and
exposition of the transport models and relevant parameters' effect on rim
widths.

@@

% TODO Choose names for these models and refer to them consistently, throughout
% TODO define ALL symbols, synchrotron constants, etc
\note[Aaron]{\citet{blandford1987} and other papers take a much more thorough
tack in deriving the relevant transport equations, drawing specifically from
plasma physics / DSA assumptions -- I suppose that much material is not
relevant or condensed into our diffusion coefficient $D$ (w/ stated Bohm
diffusion).  Is na\"ively citing generalized ``transport'' is sufficient here?
E.g., there is often a term of form $(E/3) (\del\cdot\vec{v}) (\ptl f/\ptl E)$,
neglected for steady downstream velocity (i.e., $\del\cdot\vec{v}=0$), which
would not arise out of our equations as stated.
See, e.g., equation (9) of \citet{skilling1975}.}
% Transport fundamentals
The energy and space distribution of electrons at a supernova remnant
controls the synchrotron rims we see in X-ray and radio.  We model electron
advection and diffusion from initial injection at the remnant's forward shock
assuming 1-D steady-state plane transport, with spatially homogeneous and
isotropic diffusion, as following the equation:
\begin{equation}
    v_d \frac{\ptl f}{\ptl x} - D \frac{\ptl^2 f}{\ptl x^2} = C .
\end{equation}
Here $f = f(E,x)$ is electron distribution as a function of electron energy $E$
and downstream distance $x$ (where the forward shock is at $x=0$ and $x>0$
towards the remnant's interior); $C$ is an arbitrary source/sink term, $D$ is
the diffusion coefficient, and $v_d$ is plasma velocity downstream of the
shock.  We consider only particle transport downstream of the shock ($x \geq
0$).  The source/sink term $C$ and diffusion coefficient $D$ conveniently
encapsulate all assumptions about the accelerated electron spectrum, shock
and magnetic field structure, and time/space evolution of the particle
distribution.  More sophisticated treatments may explicitly treat magnetic
fields and diffusion across the shock, plasma streaming instabilities and
particle losses, anisotropic diffusion, the DSA process and efficiency, and
other details in great depth \citep[e.g.,][and references therein]{reville2013,
bykov2014, ferrand2014}.

@@

@@

% Bohm, Bohm-like, and MHD/turbulence-inspired diffusion
Much previous work has assumed Bohm-like diffusion in plasma downstream of SNR
shocks.  Bohm diffusion assumes that the particle mean free path $\lambda$ is
equal to the gyroradius $r_g = E/(eB)$, yielding diffusion coefficient
$D_{\mt{B}} = \lambda c / 3 = c E / (3 e B)$; here $c$ is the speed of light,
$E$ is particle energy, $e$ is the elementary charge, and $B$ is magnetic
field.  Bohm-like diffusion introduces a free prefactor $\eta$ such that
$\lambda = \eta r_g$ allows for varying diffusion; however, Bohm diffusion at
$\eta = 1$ is commonly considered a lower limit on the diffusion coefficient at
all energies.
\note[Aaron]{for self-edification, any justification / derivation of Bohm
limit?  All the papers seem to take it for granted}
Different types of MHD turbulence may give rise to a non-linear energy
scaling for diffusion coefficient \citep{giacalone1999, reynolds2004}.
Power-wavenumber spectra for Kolmogorov and Kraichnan turbulence, with a
quasi-linear approximation for particle motion,
\note[Aaron]{I don't really know what this means}
predict $D \propto E^{1/3}$ and $D \propto E^{1/2}$ respectively.
Particle gyroradii larger than field coherence length may to $D \propto E^{2}$
\note[Aaron]{Source?? Parizot mentions this in one sentence and cites nothing.
I have no idea what this means.}

% Define our diffusion coefficient, introduce fiducial energy
In our models, we consider a generalized diffusion coefficient with arbitrary
power-law dependence upon energy following, e.g., \citet{parizot2006}:
\begin{equation} \label{eq:diffcoeff}
    D(E) = \frac{\eta C_d E^\mu}{B}
         = \eta_h D_{\mt{B}}\left(E_h\right) \left(\frac{E}{E_h}\right)^\mu
\end{equation}
where $\mu$ parameterizes diffusion-energy scaling, and $\eta$ now has units
of $\mathrm{erg}^{1-\mu}$.
The right-hand side of equation~\eqref{eq:diffcoeff} introduces $\eta_h$, a
dimensionless diffusion coefficient scaled to the Bohm value at a fiducial
particle energy $E_h$.  This energy $E_h$ may be related to the emitted
synchrotron photons by taking the $\delta$-function approximation that an
electron of energy $E$ radiates at a singular frequency $\nu \propto E^2 B$ in
a magnetic field.  Note that $\eta_h$ and $\eta$ are related as
$\eta = \eta_h (E_h)^{1-\mu}$, and $\eta = \eta_h$ for Bohm-like diffusion
($\mu = 1$).

% Set choice of fiducial energy, eta_2
For subsequent analysis and model fitting, we take fiducial electron energy
$E_2 = E_h$ corresponding to a $2 \unit{keV}$ synchrotron photon and report all
model fit results in terms of $\eta_2 = \eta_h$.  Although the value of $E_2$
depends on magnetic field $B$ and may vary within the remnant, tying $\eta_h$
to a fixed observation energy gives a convenient and intuitive sense of
diffusion strength regardless of the underlying electron energies.
We also note that $\eta = \eta_2 (E_2)^{1-\mu}$.

\subsection{Electron cut-off}

% Electron cut-off energy
With a diffusion coefficient in hand, we determine the electron spectrum
cut-off energy by equating synchrotron loss and diffusive acceleration
timescales.  For low energies and small synchrotron losses (cooling time longer
than acceleration time), electrons may be efficiently accelerated; near or
above the cut-off energy, electrons will radiate or escape too rapidly to be
accelerated, so the energy spectrum drops off steeply.  The cut-off energy
adapted from \citet{parizot2006} is given as:
\begin{align}
    \Ecut =
        &\left(8.3\unit{TeV}\right)^{2/(1+\mu)}
        \left(\frac{B_0}{100 \muG}\right)^{-1/(1+\mu)} \nonumber \\
        &\times \left(\frac{v_s}{10^8 \unit{cm\;s^{-1}}}\right)^{2/(1+\mu)}
        \eta^{-1 / (1+\mu)} .
\end{align}
Note that this expression implicitly assumes (1) a strong shock with
compression ratio 4, and (2) isotropic magnetic turbulence both upstream and
downstream; see \citet{parizot2006} for a full derivation.

As the electron cut-off imposes a roll-off on SNR synchrotron flux,
estimates of the synchrotron roll-off frequency may provide an independent
observable to characterize shock conditions.
\note[Aaron]{todo: explore this?} % TODO FILL IN LATER -- NOT IMPORTANT NOW
\citet{miceli2013, yamazaki2014} looked at the synchrotron roll-off as a
diagnostic for electron spectrum cut-off behavior (whether loss or age limited)
and also infer various characteristics (particularly, $\eta > 1$ in SN 1006).
\citet{miceli2014-cloud} use azimuthal variation in synchrotron cut-off, with
other lines of evidence, to argue for the presence of a cloud interacting w/
the SW limb of SN 1006.

Speculation: could cloud interaction could be related to the sub-Bohm diffusion
observation in Sean's Filament 4?  The filament has many profiles, and looking
at Sean's data it looks like all the selections show a consistently strong drop
in FWHM.  \citet{miceli2013} argue that the concave distortion possibly
associated with the cloud is linked to a dip in synchrotron cut-off energies,
which they explain as being tied to a drop in shock velocity at the
indentation, due to the cloud.  If shock velocities are depressed, would more
diffusion / weaker B fields be necessary to explain the observed rim widths?
But we must still account for the quite strong width-energy drop-off!

@@

\subsection{Width-energy dependence and some intuition} \label{sec:energydep}

As discussed in Section~\ref{sec:intro}, width-energy dependence is key to
differentiating between loss/diffusion-limited rims and magnetically damped
rims.  \citetalias{ressler2014} parameterize rim width-energy dependence in
terms of a scaling exponent $\mE$ defined by:
\begin{equation}
    w(\nu) \propto \nu^{\mE}
\end{equation}
where $w(\nu)$ is filament FWHM as a function of observed photon frequency
$\nu$.  We may refer to observed photons interchangeably by energy or frequency
$\nu$, but $E$ is reserved for electron energy.  The exponent $\mE = \mE(\nu)$
is generally energy dependent.

We may consider advective and diffusive lengthscales for electron transport,
which naturally give rise to scaling relations:
\begin{equation} \label{eq:lad}
    l_{\mt{ad}} = v_d \tsynch \propto v_d B_0^{-3/2} \nu^{-1/2}
\end{equation}
and
\begin{equation} \label{eq:ldiff}
    l_{\mt{diff}} = \sqrt{D \tsynch} \propto \eta^{1/2} B_0^{-3/2} \nu^{(\mu-1)/4}
\end{equation}
If both diffusion and magnetic field damping are negligible (whether at a small
range of, or all, electron energies) and electrons are only loss-limited as
they advect downstream, $\mE$ attains a minimum value $\mE = -1/2$; this is the
strongest energy-dependence possible in our models.  Diffusion increases $\mE$
monotonically towards a value between $-1/4$ and $1/4$, depending on the value
of $\mu$.  In practice, $\mE$ appears to plateau at values between $-0.4$ and
$0$, with larger $\mu$ values yielding $\mE$ closer to $0$ (weaker
energy-dependence) \citepalias[Figure 3]{ressler2014}.  This may be attributed
in part to the electron energy cut-off, which limits the available electrons at
higher energies and thus thins the rims slightly, shifting $\mE$ negative
\citepalias[Figure 5]{ressler2014}.

@@

@@

We fit spectra from each region's upstream and downstream sections to an
absorbed power law model (XSPEC 12.8.1, \texttt{phabs*po}) between $0.5$--$7
\unit{keV}$ with photon index $\Gamma$, hydrogen column density $N_{\mt{H}}$,
and a normalization as free parameters.  Table~\ref{tab:spec} lists best fit
parameters and reduced $\chi^2$ values for all regions.  Spectra from thin rims
(upstream sections) are well-fit by the power law model alone; spectra from
sections downstream of the rims are generally poorly-fit, reflecting thermal
contamination primarily from \ion{Si}{13} and \ion{S}{15} He$\alpha$ line
emission at $1.85$ and $2.45$ keV.  Our best-fit photon indices ($2.4$--$3$)
and column densities ($0.6$--$0.8 \times 10^{22} \unit{cm^{-2}}$) from upstream
spectra are consistent with previous spectral fits to Tycho's nonthermal rims
\citep{hwang2002, cassam-chenai2007}.
% NOTE keep stated ranges of spectral indices, column densities up to date
% NOTE keep example region numbers up to date

@@

To estimate FWHM uncertainties, we horizontally stretched each best-fit
profile by mapping radial coordinate $x$ to
$x'(x) = x (1 + \xi (x-x_0)/(50\arcsec-x_0))$ with $\xi$ an arbitrary stretching
parameter and $x_0$ the best-fit rim center from equation~\eqref{eq:prof};
this yields a new profile $h'(x) = h(x'(x))$.
We varied $\xi$ (and hence rim FWHM) to vary each profile fit $\chi^2$ by 2.7
and took the stretched or compressed FWHMs as upper/lower bounds on our
reported FWHMs.

@@

% Model knobs and how we twiddled them
We varied three physical parameters: diffusion-energy scaling exponent $\mu$,
normalized diffusion coefficient $\eta_2$, and magnetic field strength $B_0$.
To make nonlinear fitting tractable, we fixed $\mu$ in all fits and considered
$\mu = 0$, $1/3$, $1/2$, $1$, $1.5$, and $2$; recall that $\mu = 1/3$ and $1/2$
correspond to Kolmogorov and Kraichnan turbulence.  Our fits do not consider
a damped magnetic field with the additional parameter of scale length $a_b$,
and so magnetic field strength $B_0$ is assumed constant downstream of the
shock.  Below we shall show that magnetic damping cannot explain our observed
filament widths, so we present fits assuming loss-limited rim widths only.
% TODO Edit if I add magnetic damping material

% Tycho parameters TODO change green2009 to green2014 once published in BASI
A few remnant-specific parameters enter into the model calculations.  We
adopted electron spectral index $s = 2.3$ from radio spectral index $\alpha =
0.65$ \citep{kothes2006},
\note[Aaron]{will change to $s= 2.16$ from $\alpha=0.58$ following
\citet{sun2011} on next iteration}
remnant distance $3 \unit{kpc}$ \citep[cf.][]{hayato2010}, and shock radius
$1.08 \times 10^{19} \unit{cm}$ from angular radius $240\arcsec$
\citep{green2009}.  Tycho's forward shock velocity varies with azimuth by up to
a factor of 2; we interpolated shock velocities reported by
\citet{williams2013} (rescaled to $3 \unit{kpc}$ rather than $2.3 \unit{kpc}$
to estimate individual shock velocities for each region.

@@

\begin{table*}[ht]
    % Use \tiny for manuscript; \scriptsize for 2-column
    %\tiny
    \scriptsize
    \centering
    \caption{Measured full widths at half max (FWHMs) for all regions.
             \label{tab:fwhms}}
    \input{tab-fwhms.tex}
\end{table*}

@@

The errors on FWHM measurements are typically $\abt 10\%$ or smaller,
reflecting the high quality of underlying \Chandra data as also seen in
Figure~\ref{fig:profiles}.  Scatter in FWHM measurements may be attributed in
part to (1) our profile fitting procedure, which depends on an empirically
chosen profile fit function which may also fit the rims non-uniquely, and (2)
variation in Tycho's rim morphology, also demonstrated clearly in
comparison of rims from Regions 1 and 16 in Figure~\ref{fig:profiles}.
\note[Aaron]{review paragraph wording.  This may belong in the discussion?}
